Equalizer\\Programming and User Guide

### 2009-11-18 Developer/ProgrammingGuide/paper.tex
FSAA-related documentation cleanup.
[ ] May break build
[ ] May break existing applications
[ ] Bugfix
[ ] New Feature
[x] Cleanup
[ ] Optimization
[x] Documentation

    viewport [ viewport ]            # wrt parent compound, sort-first
    range    [ float float ]         # DB-range for sort-last
    pixel    [ int int ]             # pixel decomposition (step size)
    subpixel [ int int ]			 # subpixel decomposition (index size)
    eye      [ CYCLOP LEFT RIGHT ]   # monoscopic or stereo view
    zoom     [ float float ]         # up/downscale of parent pvp
    period   int                     # DPlex period, every nth frame rendered
    phase    int                     # DPlex phase, when to start rendering

>>>>

    viewport [ viewport ]            # wrt parent compound, sort-first
    range    [ float float ]         # DB-range for sort-last
    pixel    [ int int int int ]     # pixel decomposition (x y w h)
    subpixel [ int int ]	     # subpixel decomposition (index size)
    eye      [ CYCLOP LEFT RIGHT ]   # monoscopic or stereo view
    zoom     [ float float ]         # up/downscale of parent pvp
    period   int                     # DPlex period, every nth frame rendered
    phase    int                     # DPlex phase, when to start rendering
